Proof of uniform convergence for a cell-centered AP discretization of the hyperbolic heat equation on general meshes

### 2015-04-01 Answers_for_reviewers.tex

\title{Answers for the Reviewers  for the paper "Proof of uniform convergence for a cell-centered AP discretization of the hyperbolic heat equation on general meshes"}

\author{Emmanuel Franck\footnotemark[1] \footnotemark[2],
C. Buet \footnotemark[3], 
B. Despr\'es\footnotemark[4], 
T. Leroy\footnotemark[4] \footnotemark[3]
}
 \footnotetext[1]{INRIA Nancy Grand-Est and IRMA Strasbourg}
 \footnotetext[3]{CEA, DAM, DIF, F-91297 Arpajon Cedex,France}
 \footnotetext[4]{Laboratoire Jacques-Louis Lions,
  Universit\'e Pierre et Marie Curie,
  75252 Paris Cedex 05,
  France}
\footnotetext[2]{Email adress: emmanuel.franck@inria.fr}

\maketitle

\section{Answers for the report 2M}

\begin{itemize}
\item A massive overuse of ``Constant C'' and the issue of the estimates? time-dependence
\begin{itemize}
\item Page 5 we have modified the constant for the 1D regularity mesh
\item We have correct the constant in the proposition 2.5 page 8
\item Page 7 : we have corrected the constant in the proposition 2.2 page 7
\item Point 2-1:
\item Point 2-2:
\item Page 8 : corrected.
\item Page 11 -1: It is the mesh constant, now explicitly given.
\item Page 11 -2: (28)$\to$(29), corrected.
\item Page 11 -3: We have change ``the Cauchy-Schwarz inequality'' to ``the Jensen inequality''.
\item Pages 11-12: all the constants have been given.
\item Pages 20-27 -1:
\item Pages 20-27 -2:
\item Pages 20-27 -3:
\item Page 36 : The conflict for the notation have been corrected. For the solution there are not reference, we have construct this solution using a separation of the variable. we have added the details.
\item Last point: in 1D we have explicit all the constant. We obtain time-exponential rate as you expect. Numerically we constat a a time-linear rate, we have added a remark in the numerical part at this subject. 
\end{itemize}
\end{itemize}
\begin{itemize}
\item Comments and suggestions
\begin{itemize}
\item 1: We have added two subsections : "Precisions on AP discretizations" and "Organisation of the proof"
\item 2: we have added 2 sentences about the 2D Riemann problem and the nodal scheme. 
\item 3: We have added a sentence to explain why we use this formulation of the scheme and not the classical Gosse-Toscani scheme. For the remark about " the authors choose to renounce to the well- balanced property of the original 1D Gosse-Toscani scheme (except on uniform Cartesian grids) while retaining only its AP character" it is not clear that we say that. Indeed the scheme is well balanced for a subset of steady states (see annex of the paper "design of AP scheme ..."): the steady state associated to $u=Cts$ and $p$ linear. This property is perhaps impotent for the uniform convergence. At the end we renounce only to the steady states associated to $\nabla{u}=\nabla\times \phi$ with $\phi$ a potential. 
\item 4: We have correct this part introducing $v$ to obtain a not confusing proof.
\item 5: We have replaced is $\mathbf{u}^{\eps}$ by $u^{\eps}$
\item 6 : We have replaced the proposition 2.8 by the Lemma 2.8
\item 7 : We have added the reference on the paper "Time asymptotic high order ..." at the end of the 2D in the numerical results.
\item 8 : We have corrected the proposition 
\item 9 : We have added the missing "("
\end{itemize}
\item Minor issues and Typos
\begin{itemize}
\item 1: We have replaced $P^0$ by "first order"
\item 2 : we have corrected this sentence 
\item 3 : we have corrected this sentence 
\item 4 : we have corrected this sentence. (17) correspond to the scheme not the smooth data.
\item 5 : we have corrected this sentence. 
\item 6 : we have corrected your two remarks in this page 
\item 7 : we have corrected this sentence. 
\item 8: We have replaced $\gamma$ by $\tau$ in the numeric part.
\item 9: The date for the L. Gosse paper have been modified. for the S. Jin article we have copy the reference written on the website of S. Jin 
\end{itemize}
\end{itemize}
\end{document}

### 2015-04-01 Corrected_version.tex
last correction thomas

We define a  threshold value $\varepsilon_{\rm thresh} $
by  $\varepsilon_{\rm thresh}  ^{-b}h^c=
\eps_{\rm thresh}^a$. So either $\eps\leq \varepsilon_{\rm thresh} $
so that $\min
\left(
 \varepsilon ^{-b}h^c,
\eps^a
\right)\leq \varepsilon_{\rm thresh} =h^{\frac{ac}{a+b}  }$, or 
$\eps\geq \varepsilon_{\rm thresh} $ and the same bound is obtained by 
taking the other term as the minimum.
And since $d\geq c$, one gets the abstract bound
$
\| P_h^\varepsilon - P^\varepsilon   \|
\leq
3Ch^{\frac{ac}{a+b}  }
$ which ends the proof.
\end{proof}

@@

We denote by $\V^{\eps}(t,x)=\left(p^{\eps}(x,t),
u^{\eps}(x,t)\right)$ the solution of the hyperbolic heat equations $P^\eps$ and by
$\V^{\eps}_h(t)=
\left( \sum_{j\in \mathbb Z} p_j^{\eps}(t) {1}_{\Omega_j} ,  \sum_{j\in \mathbb Z} u_j^{\eps}(t) {1}_{\Omega_j} \right)$ the solution of the JL-(b) scheme $P_h^\eps$. Similarly  we  reconstruct
similar quantities from the diffusion scheme: it yields 
$\W^\eps(t,x)=\left(p(x,t),\varepsilon v(x,t)\right)$ 
which is the 
solution of the diffusion limit
$P^0$ (\ref{difffff})-(\ref{eq:diff-v}),
 and  $\W_h^\eps(t)= \left( \sum_{j\in \mathbb Z} p_j(t) {1}_{\Omega_j} ,
\varepsilon \sum_{j\in \mathbb Z} v_j(t)  {1}_{\Omega_j} \right)$ which is
the
solution of the diffusion scheme $P_h^0$ (\ref{schemadifff})-(\ref{eq:vv}). 
For simplicity we choose a final time $T>0$.
All  error estimates will be given for 
$t\leq T$, either
in the norm
$\|f(t)\|_{L^\infty([0,T];L^2(\mathbb{R}))}$, or mostly in the norm
$\|f\|_{L^2([0,T]\times \mathbb{R})}$

@@

We  use the convention that the quadratic norm
of any cell centered quantity $f=(f_j)_{j\in {\rm Cells}}$ is
$\|f\|_{L^2(\Omega)}=\sqrt{\sum_j |\Omega_j| |f_j|^2   }$, while the quadratic
norm of any vertex based quantity $g=(g_r)_{r\in {\rm Vertices}}$ is
$\|g\|_{L^2(\Omega)}=\sqrt{\sum_r |V_r| |g_r|^2   }$.
Useful  quantities  are
\begin{itemize}
\item $\mathbf V_h^\eps=\left(  \sum_{j\in Cells} p^\eps_j 1_{\Omega_j} , \sum_{j\in Cells} \uu^\eps_j  1_{\Omega_j} \right) $ is the solution of $\mathbf P_h^\eps$.
\item 
$\mathbf V^\eps=\left(p^\eps, \uu^\eps  \right)$ is the solution of $\mathbf P^\eps$,
\item $\mathbf W_h^\eps=\left(  \sum_{j\in Cells}  p^\eps_j 1_{\Omega_j} ,  \sum_{j\in Cells}  \uu^\eps_j  1_{\Omega_j}  \right) $ is the solution of $\mathbf{DA}_h^\eps$.
Notice that an abuse of notations is been made with the solution
of $\mathbf P_h^\eps$.
\item $\mathbf W^\eps= \left( p ,-\frac\eps\sigma \nabla p  \right) $ is the solution of $\mathbf P^0$.
\end{itemize}
With these notations,  (\ref{ine3}) is rewritten as
\begin{equation} \label{eq:enc22}
\|\W^\eps-\mathbf V^\eps\|
_{ L^2([0,T]\times L^2(\Omega)   ) } \leq C \eps.
\end{equation}
The initialization stage yields 
\begin{equation}\label{constant_init}
\left\{
\begin{aligned}
&\| \mathbf{V}_0 - \mathbf{V}^{\eps}_h(0)\|_{L^2(\Omega)} \leq C_0 h \|  \mathbf V ^\eps_0 \|_  { H^1(\Omega)  } ,\\
&\| \mathbf{W}_0 - \mathbf{W}^{\eps}_h(0)\|_{L^2(\Omega)} \leq C_0 h \|  \mathbf W ^\eps_0 \|_  { H^1(\Omega)  } .
\end{aligned}
\right.
\end{equation}

>>>>

We define a  threshold value $\varepsilon_{\rm thresh} $
by  $\varepsilon_{\rm thresh}  ^{-b}h^c=
\eps_{\rm thresh}^a$. So either $\eps\leq \varepsilon_{\rm thresh} $
so that $\min
\left(
 \varepsilon ^{-b}h^c,
\eps^a
\right)\leq \varepsilon_{\rm thresh}^a =h^{\frac{ac}{a+b}  }$, or 
$\eps\geq \varepsilon_{\rm thresh} $ and the same bound is obtained by 
taking the other term as the minimum.
And since $d\geq c$, one gets the abstract bound
$
\| P_h^\varepsilon - P^\varepsilon   \|
\leq
3Ch^{\frac{ac}{a+b}  }
$ which ends the proof.
\end{proof}

@@

We denote by $\V^{\eps}(t,x)=\left(p^{\eps}(x,t),
u^{\eps}(x,t)\right)$ the solution of the hyperbolic heat equations $P^\eps$ and by
$\V^{\eps}_h(t,x)=
\left( \sum_{j\in \mathbb Z} p_j^{\eps}(t) {1}_{\Delta x_j}(x) ,  \sum_{j\in \mathbb Z} u_j^{\eps}(t) {1}_{\Delta x_j}(x) \right)$ the solution of the JL-(b) scheme $P_h^\eps$, in which ${1}_{\Delta x_j}(x)=1$ if $x\in\Delta x_j$ and $0$ elsewhere. We  reconstruct
similar quantities from the diffusion scheme: it yields 
$\W^\eps(t,x)=\left(p(x,t),\varepsilon v(x,t)\right)$ 
which is the 
solution of the diffusion limit
$P^0$ (\ref{difffff})-(\ref{eq:diff-v}),
 and  $\W_h^\eps(t,x)= \left( \sum_{j\in \mathbb Z} p_j(t) {1}_{\Delta x_j}(x) ,
\varepsilon \sum_{j\in \mathbb Z} v_j(t)  {1}_{\Delta x_j}(x) \right)$ which is
the
solution of the diffusion scheme $P_h^0$ (\ref{schemadifff})-(\ref{eq:vv}). 
For simplicity we choose a final time $T>0$.
All  error estimates will be given for 
$t\leq T$, either
in the norm
$\|f(t)\|_{L^\infty([0,T];L^2(\mathbb{R}))}$, or mostly in the norm
$\|f\|_{L^2([0,T]\times \mathbb{R})}$

@@

We  use the convention that the quadratic norm
of any cell centered quantity $f=(f_j)_{j\in {\rm Cells}}$ is
$\|f\|_{L^2(\Omega)}=\sqrt{\sum_j |\Omega_j| |f_j|^2   }$, while the quadratic
norm of any vertex based quantity $g=(g_r)_{r\in {\rm Vertices}}$ is
$\|g\|_{L^2(\Omega)}=\sqrt{\sum_r |V_r| |g_r|^2   }$.
Useful  quantities  are
\begin{itemize}
\item $\mathbf V_h^\eps(t,\x)=\left(  \sum_{j\in Cells} p^\eps_j(t) 1_{\Omega_j}(\x) , \sum_{j\in Cells} \uu^\eps_j(t)  1_{\Omega_j}(\x) \right) $ is the solution of $\mathbf P_h^\eps$.
\item 
$\mathbf V^\eps(t,\x) =\left(p^\eps, \uu^\eps  \right)(t,\x)$ is the solution of $\mathbf P^\eps$,
\item $\mathbf W_h^\eps(t,\x) =\left(  \sum_{j\in Cells}  p^\eps_j(t) 1_{\Omega_j}(\x) ,  \sum_{j\in Cells}  \uu^\eps_j(t)  1_{\Omega_j} (\x) \right) $ is the solution of $\mathbf{DA}_h^\eps$.
Notice that an abuse of notations is been made with the solution
of $\mathbf P_h^\eps$.
\item $\mathbf W^\eps (t,\x) = \left( p ,-\frac\eps\sigma \nabla p  \right) (t,\x)$ is the solution of $\mathbf P^0$.
\end{itemize}
With these notations,  (\ref{ine3}) is rewritten as
\begin{equation} \label{eq:enc22}
\|\W^\eps-\mathbf V^\eps\|
_{ L^2([0,T]\times L^2(\Omega)   ) } \leq C \eps.
\end{equation}
The initialization stage yields 
\begin{equation}\label{constant_init}
\left\{
\begin{aligned}
&\| \mathbf{V}_0 - \mathbf{V}^{\eps}_h(0)\|_{L^2(\Omega)} \leq C_0 h \|  \mathbf V ^\eps_0 \|_  { H^1(\Omega)  } ,\\
&\| \mathbf{W}_0 - \mathbf{W}^{\eps}_h(0)\|_{L^2(\Omega)} \leq C_0 h \|  \mathbf W ^\eps_0 \|_  { H^1(\Omega)  } .
\end{aligned}
\right.
\end{equation}
